Which PMV model should you use? Comparison of the ISO 7730:2005 and ASHRAE 55:2023 PMV models

### 2024-08-29 Manuscript/src/sections/titleAbstract.tex
feat: updated the results using v_r instead of v

    \title{PMV: Comparing the prediction accuracy of ISO 7730:2005 and ASHRAE 55:2023}
    % alternatives PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?
    % alternatives ISO 7730:2005 vs ASHRAE 55:2023: A comparison of the accuracy of the two implementations of the PMV model

    \author[label1,label2]{Federico Tartarini\corref{mycorrespondingauthor}}
    \ead{federicotartarini@berkeley.edu}
    \author[label3]{Stefano Schiavon}

    \address[label1]{Berkeley Education Alliance for Research in Singapore, Singapore}
    \address[label2]{Heat and Health Research Incubator, Faculty of Health and Medicine, University of Sydney, Sydney, AU}
    \address[label3]{Center for the Built Environment, University of California, Berkeley, CA, USA}

@@

%        Being relatively simple to calculate and included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730} although it has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one of which is currently used in the \gls{55}.
        The \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion for many users who often struggle to determine which model is most appropriate for their needs.

        We compared the accuracy of the two main \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that the use of the \ac{pmv-ce} provides no significant improvement over the original \ac{pmv} in predicting thermal sensation, despite its increased complexity and computational resources needed to calculate the results.
        Surprisingly, the bias of the \ac{pmv-ce} model was greater (a higher number is negative) than the \ac{pmv} when we only analyzed the entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\sec}.

        Based on our results, we recommend using the original \ac{pmv} instead of the \ac{pmv-ce} and we suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        The \ac{pmv} model cannot determine the degree to which people are dissatisfied.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, our results show that the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale to determine how people perceive their thermal environment.
    \end{abstract}

>>>>

    \title{Which PMV model should you use? Comparison of the ISO 7730:2005 and ASHRAE 55:2023 PMV models}
    % alternatives PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?
    % alternatives ISO 7730:2005 vs ASHRAE 55:2023: A comparison of the accuracy of the two implementations of the PMV model

    \author[label1,label2]{Federico Tartarini\corref{mycorrespondingauthor}}
    \ead{federico.tartarini@sydney.edu.au}
    \author[label3]{Stefano Schiavon}

    \address[label1]{University of Sydney, Sydney, AU}
    \address[label2]{Berkeley Education Alliance for Research in Singapore, Singapore}
    \address[label3]{Center for the Built Environment, University of California, Berkeley, CA, USA}

@@

%        Being relatively simple to calculate and included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730}.
        It has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one is the \ac{pmv-ce}.
        The \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion.
%        for many users who often struggle to determine which model is most appropriate for their needs.
        Which model is more accurate?
        Which model should you use?

        We compared the accuracy of the two \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        Based on our results, we recommend using the original \ac{pmv} instead of the \ac{pmv-ce}, since the \ac{pmv-ce} provides no significant improvement over the original \ac{pmv} in predicting thermal sensation, despite its increased complexity.
%        Surprisingly, the bias of the \ac{pmv-ce} model was greater (a higher number is negative) than the \ac{pmv} when we only analyzed the entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\sec}.
        We suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$ since the \ac{pmv} model cannot determine the degree to which people are dissatisfied.
%        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale instead of the thermal sensation scale.
    \end{abstract}
